Constant Partying: \\ Introducing a Generic Toolkit for Recursive Partitioning in R

### 2014-03-18 pkg/partykit/inst/NUS-2014/constparty.Rnw
touch-ups in graphics, added some FIXMEs
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@495 255f4249-2263-4417-b1ea-8498779e27a7

<<Morgen+Sonquist-1963>>=
ms63d <- data.frame(
  earnings = numeric(),
  ethnicity = factor(, levels = 1:2, labels = c("other", "afam")),
  age = numeric(),
  occupation = factor(, levels = 1:2, labels = c("other", "farmer")),
  education = factor(, levels = 1:4, labels = c("elementary", "highschool", "college", "university"), ordered = TRUE)
)

@@

<<ms63-plot1, fig=TRUE>>=
plot(py)
@

@@

\setkeys{Gin}{width=1.15\textwidth}
<<ms63-plot2, fig=TRUE, height=8, width=14>>=
plot(ms63p, drop = TRUE)
@

@@

\setkeys{Gin}{width=1.1\textwidth}
\hspace*{-0.4cm}%
<<Titanic-pmml-visualization, fig=TRUE, height=10, width=16>>=
plot(pm)
@

@@

@@

@@

Hothorn T, Zeileis A (2014).
 \textit{partykit: A Toolkit for Recursive Partytioning.}
 R~package vignette version~0.2-0.
 URL~\url{http://CRAN.R-project.org/package=partykit}

>>>>

<<Morgen+Sonquist-1963>>=
ms63d <- data.frame(
  earnings = numeric(),
  ethnicity = factor(, levels = 1:2, labels = c("cauc", "afam")),
  age = numeric(),
  occupation = factor(, levels = 1:2, labels = c("other", "farmer")),
  education = factor(, levels = 1:4, labels = c("elementary", "highschool", "college", "university"), ordered = TRUE)
)

@@

\setkeys{Gin}{width=0.65\textwidth}
\begin{center}
<<ms63-plot1, fig=TRUE>>=
plot(py)
@
\end{center}

@@

\setkeys{Gin}{width=1.2\textwidth}
\hspace*{-1cm}%
<<ms63-plot2, fig=TRUE, height=8, width=14>>=
plot(ms63p, drop = TRUE)
@

@@

\vspace*{-0.2cm}

\setkeys{Gin}{width=1.1\textwidth}
\hspace*{-0.4cm}%
<<Titanic-pmml-visualization, fig=TRUE, height=12, width=17>>=
plot(pm)
@

@@

FIXME: partykit still only on R-Forge

@@

FIXME: Show code for completeness?

FIXME: Change/update/enhance references?

@@

Hothorn T, Zeileis A (2014).
 \textit{partykit: A Toolkit for Recursive Partytioning.}
 R~package vignette version~0.8-0.
 URL~\url{http://CRAN.R-project.org/package=partykit}
